---
title: "Résumé"
description: |
  Angela M. Zoss, Ph.D.
output:
  distill::distill_article:
    toc: true
    toc_depth: 3  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<aside>[PDF version]('AngelaZoss-Resume-2022-01-16.pdf')</aside>

```{r}
library(htmltools)
htmltools::tags$script(src = "https://cdn.jsdelivr.net/npm/public-google-sheets-parser@latest")
htmltools::includeScript("buildresume.js")
```

## Education

::: {#ed}
:::

## Work Experience

::: {#work}
:::

## Publications

### Theses/Dissertations

::: {#theses}
:::

### Journal Articles

::: {#jrnl}
:::

### Book Chapters

::: {#bkchp}
:::

### Conference Papers

::: {#conf}
:::        

### White Papers

::: {#whitepapers}
:::

## Projects

::: {#proj}
:::

## Certifications

::: {#cert}
:::

## Skills and Experience

::: {#skills}
:::

## Awards/Honors

::: {#awards}
:::

## Teaching Activities and Presentations

### Semester-Length Teaching Experiences

::: {#courses}
:::

### Extended Workshop Instruction Experiences

::: {#long-workshops}
:::

### Presentations at Conferences, Professional Gatherings

::: {#presentations}
:::

### Guest Lectures

::: {#lectures}
:::

### Short-form Instruction Experience

::: {#workshops}
:::
